---
title: "Exploring Amphibian Populations"
description: |
  Exploring the mountain yellow-legged frog population in southern Sierra Nevada
author:
  - name: Larissa Neilson
    url: {}
date: 2021-03-07
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(patchwork)
library(lubridate)
library(readxl)
```

```{r}
# Read in Sierra amphibians data using `read_excel()`
amphibians <- (read_excel(here("sierra_amphibians.xlsx"))) %>% 
  clean_names()
```

```{r}
# Pull the year using `lubridate()` and wrangle to create desired subset
amphibians_ramu <- amphibians %>% 
  mutate(date = ymd(survey_date)) %>% 
  mutate(survey_year = year(date)) %>%
  filter(amphibian_species == "RAMU") %>%
  filter(amphibian_life_stage != "EggMass")
```

```{r}
# Count by life stage and weight results properly
ramu_count <- amphibians_ramu %>% 
  group_by(survey_year) %>% 
  count(amphibian_life_stage, wt = amphibian_number)
```

```{r}
# Create ggplot showing frog counts over the years across life stages
ramu_plot <- ggplot(data = ramu_count, aes(x = survey_year, y = n)) +
  geom_col(fill = "darkseagreen3", color = "darkseagreen4") +
  facet_wrap(~ amphibian_life_stage) +
  labs(x = NULL , y = "Rana muscosa count") +
  ggtitle("(a)") +
  geom_text(aes(label = n), vjust = -0.2, color = "black", size = 2) +
  theme_minimal()
```

```{r}
# Wrangle to create a separate subset for second visualization
amphibians_ramu_2 <- amphibians %>% 
  mutate(date = ymd(survey_date)) %>% 
  mutate(survey_year = year(date)) %>%
  filter(amphibian_species == "RAMU") %>%
  filter(amphibian_life_stage == c("Adult", "SubAdult"))
```

```{r}
# Find the five lakes with the greatest observed counts of frog adults and subadults
ramu_count_combined <- amphibians_ramu_2 %>%
  count(lake_id, wt = amphibian_number) %>%
  slice_max(n, n = 5) %>% 
  relocate(n) %>% 
  mutate(lake_name = "Lake") %>% 
  unite("lake_id_new", lake_name:lake_id, sep = " ")
```


```{r}
# Create ggplot showing the five lakes with the greatest observed counts of frogs over the years
ramu_plot_2 <- ggplot(data = ramu_count_combined, aes(x = fct_reorder(lake_id_new, n), y = n)) +
  geom_col(fill = "cadetblue3", color = "cadetblue4") +
  labs(x = NULL, y = "Rana muscosa count") +
  ggtitle("(b)") +
  geom_text(aes(label = n), hjust = -0.1, color = "black", size = 2.5) +
  coord_flip() +
  theme_minimal()
```

### Frog counts by life stage over time, and the top 5 lakes with the greatest observed frog counts over time

```{r}
ramu_plots <- (ramu_plot / ramu_plot_2) & theme_minimal()

ramu_plots
```

**Figure 1.** (a) Total number of *Rana muscosa* adults, subadults, and tadpoles observed in the southern Sierra Nevada from 1995-2002. (b) The five lakes with the greatest number of *Rana muscosa* adults and subadults from 1995-2002. Data: Knapp et al. 2020. 

#### Data citation:

Knapp, R.A., C. Pavelka, E.E. Hegeman, and T.C. Smith. 2020. The Sierra Lakes Inventory Project: Non-Native fish and community composition of lakes and ponds in the Sierra Nevada, California ver 2. Environmental Data Initiative. https://doi.org/10.6073/pasta/d835832d7fd00d9e4466e44eea87fab3

