---
title: "Spatial Analysis"
description: |
  Visualizing Oil Spill Incidents in California (2008)
author:
  - name: Larissa Neilson
date: 02-21-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE)

library(tidyverse)
library(here)
library(sf)
library(tmap)
library(shinyjs)
```

```{r}
# Read in CA county outlines
ca_counties <- read_sf(here("ca_counties","CA_Counties_TIGER2016.shp"))

# Only keep required attributes
ca_subset <- ca_counties %>% 
  select(NAME, ALAND) %>% 
  rename(county_name = NAME, land_area = ALAND)

# Check CRS in console

```

```{r}
# Read in oil spill data
oil_spill <- read_sf(here("Oil_Spill_Incident_Tracking","Oil_Spill_Incident_Tracking_%5Bds394%5D.shp"))

# Check CRS in console
```

### Interactive tmap showing the oil spill incidents in California

```{r}
# Make exploratory tmap

# Set viewing mode to interactive
tmap_mode(mode = "view")

tm_shape(ca_subset) +
  tm_fill() +
  tm_shape(oil_spill) +
  tm_dots()
```

**Figure 1.** Inland oil spill incidents in California (2008). Most spills are concentrated in central and southern California.

### Chloropleth map showing the counts of oil spill incidents by county

```{r}
# Join datasets
ca_oil_spill <- ca_subset %>% 
  st_join(oil_spill)

# Find the counts
oil_spill_counts <- ca_oil_spill %>% 
  count(county_name)

# Make chloropleth map
ggplot(data = oil_spill_counts) +
  geom_sf(aes(fill = n), color = "white", size = 0.1) +
  scale_fill_gradientn(colors = c("lightyellow", "orange", "red")) +
  theme_void() +
  labs(fill = "Number of Oil Spill Incidents")
```

**Figure 2.** Chloropleth map showing the number of oil spill incidents by county in 2008. Los Angeles county seems to have the highest number of oil spills incidents.
