---
title: CV
name: Larissa
surname: Neilson
position: "Master's candidate"
location: "Goleta, CA"
phone: (818) 282-6200
email: "eneilson@bren.ucsb.edu"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

### Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bren School of Environmental Science & Management", "2020-present", "Santa Barbara, CA", "Master of Environmental Science & Management",
  "California State University, Monterey Bay", "2015-2019", "Seaside, CA", "Bachelor of Environmental Science") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

______________________________________________________________________________

### Research Experience

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "University of California, Santa Barbara", "2020-present", "Santa Barbara, CA", "Research Assistant") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

Supervisor - Anastasia Quintana

Duties:

• Conducting literature reviews to inform postdoctoral research on compliance in small-scale fisheries

• Identifying governance types in 75+ managed access areas throughout Indonesia, Brazil, Honduras, Micronesia, Mozambique, and the Philippines & creating a dataset with this information

• Managing the social media presence of Dr. Anastasia Quintana to help expand her network

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Monterey Bay Aquarium Research Institute", "June - August 2018", "Moss Landing, CA", "Undergraduate Researcher") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

Supervisors - Dr. Steve Litvin, Dr. Jim Barry

• Quantified & analyzed the effects of present & future climate change and ocean acidification associated with upwelling on juvenile *Haliotis rufescens* (red abalone) through an 8-week live experiment

• Created & maintained Excel worksheets with abalone measurement parameters for all 300+ individuals

• Conducted extensive image and statistical analysis using experimental data from 300+ individuals  

• Presented results to audiences ranging from 5-200 people at various conferences and symposiums including SACNAS and the California Central Coast Chapter of The Wildlife Society’s Annual Symposium

______________________________________________________________________________

### Volunteer Experience

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "University of California, Santa Cruz Fort Ord Natural Reserve", "June - July 2019", "Marina, CA", "Herptile Population Monitoring Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Surveyed & monitored *Phrynosoma blainvillii* (Blainville’s horned lizard) populations by catching and PIT tagging individuals

• Handled live animals & collected data in the field using measurement equipment to capture parameters such as weight and snout-vent length

• Informed the dissertation of Danielle Davis (UCSC) looking at temporal differences in horned lizard population over time at the UCSC FONR

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "California State University, Monterey Bay", "March - May 2019", "Seaside, CA", "Dungeness Crab Population Project Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Collected megalopa crab population data for a California Department of Fish and Wildlife (CDFW) monitoring project aiming to inform Dungeness crab fisheries

• Gathered & stored megalopa crab samples once a week from a trap at the Moss Landing Marine Labs boat dock

• Organized & maintained crab sample counts and measurement data into project notebook

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Return of the Natives", "January - May 2018", "Seaside, CA", "Educational Outreach Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Co-taught an environmental education outreach program for 4th-5th grade elementary classes at local, lower-income schools

• Prepared & organized lecture material for environmental science presentations adequate for 10-12-year old’s. Topics included photosynthesis, waste management, and climate change

• Assisted in organizing multiple beach planting community events with the goal of reintroducing 200+ native plants across ~5 species back to vulnerable dune ecosystems

______________________________________________________________________________

### Skills and certifications

**Computer**: Microsoft Office (Word, Excel, PowerPoint), R, Google Suite, Outlooks

**Language**: Bilingual (Spanish), public speaking, problem resolution, team building

**Certifications**: CITI Responsible Research & Conduct, Trimble GPS


