---
name: Larissa
surname: Neilson
position: "Master's candidate"
phone: (818) 282-6200
email: "eneilson@bren.ucsb.edu"
output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

### Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bren School of Environmental Science & Management", "2020-2022", "Santa Barbara, CA", "Master of Environmental Science and Management",
  "California State University, Monterey Bay", "2015-2019", "Seaside, CA", "B.S. in Environmental Science") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

______________________________________________________________________________

### Research Experience

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "University of California, Santa Barbara", "2020-present", "Santa Barbara, CA", "Graduate Research Assistant") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

Supervisor - Anastasia Quintana

• Conducting literature reviews to inform postdoctoral research on compliance in small-scale fisheries

• Identifying governance types in 75+ managed access areas throughout Indonesia, Brazil, Honduras, Micronesia, Mozambique, and the Philippines & creating a dataset with this information

• Managing the social media presence of Dr. Anastasia Quintana to expand her network

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Monterey Bay Aquarium Research Institute", "June - August 2018", "Moss Landing, CA", "Undergraduate Researcher (NSF funded)") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

Supervisors - Dr. Steve Litvin, Dr. Jim Barry

• Quantified and analyzed the effects of present & future climate change and ocean acidification associated with upwelling on juvenile red abalone through an 8-week live experiment

• Created and maintained Excel spreadsheets with various abalone measurements from 300+ individuals

• Conducted extensive image and statistical analysis using experimental data from 300+ individuals  

• Presented results to audiences ranging from 10-200 people at various conferences and symposiums including SACNAS and the California Central Coast Chapter of The Wildlife Society’s Annual Symposium (2018)

______________________________________________________________________________

### Field and Outreach Experience

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "University of California, Santa Cruz Fort Ord Natural Reserve", "June - July 2019", "Marina, CA", "Herptile Population Monitoring Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Surveyed and monitored Blainville’s horned lizard populations by catching and PIT tagging individuals

• Collected data using field measurement equipment to capture parameters such as weight & snout-vent length

• Informed the dissertation of a Ph.D. student quantifying temporal differences in horned lizard population over time

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "California State University, Monterey Bay", "March - May 2019", "Seaside, CA", "Dungeness Crab Population Project Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Collected megalopa crab population data for a California Department of Fish and Wildlife (CDFW) project aiming to inform Dungeness crab fisheries on local populations

• Gathered and stored megalopa crab samples once a week from a crab trap at the Moss Landing Marine Labs boat dock

• Organized and maintained crab sample counts and measurement data in the project notebook

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Return of the Natives", "January - May 2018", "Seaside, CA", "Educational Outreach Volunteer") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

• Co-taught an environmental education program for elementary classes at local, low-income schools

• Prepared and organized lecture material for environmental science presentations adequate for 10-12-year olds. Topics included photosynthesis, plastics, and climate change

• Assisted in organizing multiple beach planting community events with the goal of reintroducing 200+ native plants across ~5 species back to vulnerable dune ecosystems

______________________________________________________________________________

### Skills and certifications

**Computer**: R, GitHub, Microsoft Office (Word, Excel, PowerPoint), Google Suite

**Language**: Bilingual (Spanish), public speaking, problem resolution, team building

**Certifications**: CITI Responsible Research & Conduct, Trimble GPS

