---
title: "Raster data"
description: |
  Exploring Cetacean Species Richness in California
author:
  - name: Larissa Neilson
date: 02-24-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE)

library(raster)
library(tidyverse)
library(here)
library(sf)
library(fasterize)
library(rnaturalearth)
```

```{r}
# Read in all cetacean .tif files
cetacean_files <- list.files(path = here("ca_cetaceans"), pattern = ".tif", all.files = TRUE, full.names = TRUE)
```

```{r}
# Stack cetacean_files
ca_cetaceans <- stack(cetacean_files)

# Create threshold
is_present <- function(x, thresh = .6) {
  y <- ifelse(x >= thresh, 1, TRUE)
  return(y)
}

presence <- calc(ca_cetaceans, fun = is_present)

presence1 <- calc(presence, fun = sum, na.rm = TRUE)
```

```{r, include = FALSE}
# Download CA coast sf
coastline10 <- ne_download(scale = 10, type = "coastline", category = "physical", returnclass = "sf")
```

### Species richness

```{r}
# Not shown because a message would persist in my knitted html; this was my code to download the CA coast sf:

# coastline10 <- ne_download(scale = 10, type = "coastline", category = "physical", returnclass = "sf")

# Convert to df
cetaceans_df <- raster::rasterToPoints(presence1) %>%
  as.data.frame()

# Map it
ggplot() +
geom_raster(data = cetaceans_df, aes(x = x, y = y, fill = layer)) +
  geom_sf(data = coastline10) +
  coord_sf(xlim = c(-125, -115), ylim = c(32, 38)) +
  scale_fill_gradient(low = NA, high = "blue") +
  labs(x = "Longitude", y = "Latitude") +
  labs(fill = "# of cetacean species") +
  ggtitle("Cetacean Species Richness on California's Coast") +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white'))
```

**Figure 1.** Cetacean species richness. Species richness was calculated using a probability threshold of >= 0.6, indicating values at which a species is considered to be present. Raster stack was converted into a data frame and plotted over an outline of California's coast (data from the `rnaturalearth` package). Cetacean species richness seems to be highest in California's southern coast.

### Data citation

Kaschner, K., Rius-Barile, J., Kesner-Reyes, K., Garilao, C., Kullander, S., Rees, T., & Froese, R. (2016). AquaMaps: Predicted range maps for aquatic species. www.aquamaps.org

