---
title: "Parameter Estimation"
description: |
  Estimating global wild fish catch using non-linear least squares
author:
  - name: Larissa Neilson
    url: {}
date: 2021-03-14
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
  )
library(tidyverse)
library(here)
library(janitor)
library(gt)
library(patchwork)
library(broom)
library(nlstools)
```

### Exploratory graph: wild catch over time

```{r}
# Read in data and wrangle to tidy format
fish_catch <- read_csv(here("fish_catch.csv")) %>% 
  slice(-1, -3, -4, -(68:71)) %>% 
  row_to_names(row_number = 1) %>%
  clean_names()

# Convert columns to numeric
fish_catch$wild_catch <- as.numeric(as.character(fish_catch$wild_catch))
fish_catch$year <- as.numeric(as.character(fish_catch$year))

# Change year values
fish_catch_zero <- fish_catch %>% 
  mutate(year_new = year - min(year))

# Look at the data
ggplot(data = fish_catch_zero, aes(x = year, y = wild_catch)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Wild catch (million tons)")
```

Wild catch over time seems to be following a logistic growth pattern.

Equation:
$P(t)=\frac{K}{1+Ae^{-kt}}$

Viewing this exploratory graph, I estimate K at ~ 95 and A at ~ 18.

```{r, include = FALSE}
# Look at the log transformed data
ggplot(data = fish_catch_zero, aes(x = year_new, y = log(wild_catch))) +
  geom_point() +
  theme_minimal() +
  labs(x = "Time", y = "Wild catch (million tons)")
```

```{r}
fish_catch_exp <- fish_catch_zero %>% 
  filter(year_new < 8.5) %>% 
  mutate(ln_catch = log(wild_catch))

# Model linear to get k estimate
lm_k <- lm(ln_catch ~ year_new, data = fish_catch_exp)
```

### Nonlinear least squares

```{r, results = FALSE}
fish_catch_nls <- nls(wild_catch ~ K/(1 + A*exp(-r*year_new)),
              data = fish_catch_zero,
              start = list(K = 95, A = 18, r = 0.05329),
              trace = TRUE
              )

# Look at the model summary
summary(fish_catch_nls)
```

```{r}
# Use broom package to get model outputs in tidier format
model_out <- broom::tidy(fish_catch_nls)
model_out

A_est <- model_out$estimate[2] # Gets the first row in the estimate column
```

Model output with estimated parameters:

$$P(t) = \frac{100.28}{1+4.32e^{-0.07t}}$$

### Visualize model over the observed values

```{r}
# Make predictions for wild catch
p_predict <- predict(fish_catch_nls)

# Bind predictions to original data frame
fish_catch_complete <- data.frame(fish_catch_zero, p_predict)

# Plot them together
ggplot(data = fish_catch_complete, aes(x = year, y = wild_catch)) +
  geom_point(cex = 1) +
  geom_line(aes(x = year, y = p_predict), color = "red") +
  labs(x = "Year", y = "Wild catch (million tons)") +
  ggtitle("Model output describing wild fish catch through time") +
  theme_minimal()
```

#### Data citation

Global wild fish catch and aquaculture production, compiled by Earth Policy Institute with 1950-2010 from U.N. Food and Agriculture Organization (FAO), Global Capture Production and Global Aquaculture Production, electronic databases, at www.fao.org/fishery/topic/16140/en.
