---
title: "Binary Logistic Regression"
description: |
  Using binary logistic regression to test the feasibility of using different tree variables to classify two Palmetto species
author:
  - name: Larissa Neilson
    url: {}
date: 2021-03-14
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(here)
library(janitor)
library(GGally)
library(broom)
library(jtools)
library(kableExtra)
```

```{r}
# Read in the data and convert columns to numeric
palmetto <- read_csv(here("palmetto.csv"),
                     col_types = cols(.default = "c")) %>%
  mutate(height = as.numeric(height)) %>%
  mutate(length = as.numeric(length)) %>%
  mutate(width = as.numeric(width)) %>% 
  mutate(green_lvs = as.numeric(green_lvs)) %>%
  clean_names()
```

```{r}
# Create smaller subset to work with and convert species to a factor
palmetto_new <- palmetto %>% 
  select(species, height, length, width, green_lvs) %>%
  mutate(species = as.factor(species))
```

### Exploratory visualization of the relationships between tree variables

```{r}
# Visualize the data in three graphs comparing the variables to height
ggplot(data = palmetto_new, aes(x = height, y = length)) +
  geom_col(aes(color = species, fill = species)) +
  labs(x = "Height (cm)", y = "Length (cm)") +
  scale_color_discrete(name = "Species",
                       labels = c("Serenoa repens", "Sabal etonia")) +
  scale_fill_discrete(name = "Species",
                      labels = c("Serenoa repens", "Sabal etonia")) +
  theme_minimal()
```

**Figure 1.** Tree height vs. canopy length for both palmetto species.

- *Serenoa repens* has a greater canopy length than *Sabal etonia* overall. Canopy length generally increases with height, but starts to decrease as the trees get taller.

```{r}
ggplot(data = palmetto_new, aes(x = height, y = width)) +
  geom_col(aes(color = species, fill = species)) +
  labs(x = "Height (cm)", y = "Width (cm)") +
  scale_fill_discrete(name = "Species", 
  labels = c("Serenoa repens", "Sabal etonia")) +
  scale_color_discrete(name = "Species",
                       labels = c("Serenoa repens", "Sabal etonia")) +
  scale_fill_discrete(name = "Species",
                      labels = c("Serenoa repens", "Sabal etonia")) +
  theme_minimal()
```

**Figure 2.** Tree height vs. canopy width for both palmetto species.

- *Serenoa repens* has a greater canopy width than *Sabal etonia* overall. Canopy width generally increases with height, but starts to decrease as the trees get taller.

```{r}
ggplot(data = palmetto_new, aes(x = height, y = green_lvs)) +
  geom_col(aes(color = species, fill = species)) +
  labs(x = "Height (cm)", y = "Green Leaf Count") +
  scale_color_discrete(name = "Species",
                       labels = c("Serenoa repens", "Sabal etonia")) +
  scale_fill_discrete(name = "Species",
                      labels = c("Serenoa repens", "Sabal etonia")) +
  theme_minimal()
```

**Figure 3.** Tree height vs. green leaf count for both palmetto species.

- *Serenoa repens* has significantly more green leaves than *Sabal etonia*. Green leaf count generally increases with height, but starts to decrease as the trees get taller.

```{r, results = FALSE}
# Palmetto binary logistic regression
palmetto_blr <- glm(species ~ height + length + width + green_lvs,
                            data = palmetto_new,
                            family = "binomial")
palmetto_blr

summary(palmetto_blr)

# 0 = Serenoa repens, 1 = Sabal etonia
```

### Binary logistic regression

**Table 1.** Binary logistic regression results. Plant height, canopy length, canopy width and green leaves are the predictor variables used to understand how they relate to probability of a palmetto being *Sabal etonia* or *Serenoa repens* (All p-values are < 2e^-16). Data: Abrahamson 2019

```{r}
# Make finalized table of blr results
palmetto_blr_tidy <- tidy(palmetto_blr)

palmetto_blr_tidy %>% 
  kbl(col.names = c(" ",
                    "Estimate",
                    "Standard Error",
                    "Statistic",
                    "P-value")) %>% 
  kable_styling("hover", full_width = F)
```

### Model accuracy

**Table 2.** Counts of correctly and incorrectly classified palmetto species based on the binary logistic regression. This model was very accurate at predicting whether the species was *Sabal etonia* or *Serenoa repens* with a 92.62% and 90.77% success rate, respectively. Data: Abrahamson 2019

```{r}
# Find probabilities
palmetto_blr_fitted <- palmetto_blr %>%
  augment(type.predict = "response")

# Make finalized table showing # correctly & incorrectly classified, and % correct
palmetto_fitted_prob <- palmetto_blr_fitted %>%
  mutate(classification = case_when(species == 2 & .fitted >= .5 ~ "Correct",
                               species == 1 & .fitted >= .5 ~ "Incorrect",
                               species == 2 & .fitted <= .5 ~ "Incorrect",
                               species == 1 & .fitted <= .5 ~ "Correct")) %>% 
  mutate(species = case_when(species == 1 ~ "Serenoa repens",
                             species == 2 ~ "Sabal etonia")) %>% 
  select(species, .fitted, classification)

palmetto_final_tbl <- palmetto_fitted_prob %>%
  group_by(species, classification) %>% 
  summarize(number_correct = n()) %>% 
  pivot_wider(names_from = classification,
              values_from = number_correct) %>%
  mutate(percent_correct = case_when(species == "Sabal etonia" ~ (5701/(5701+454)*100),
                                     species == "Serenoa repens" ~ (5548/(5548+564)*100)))

palmetto_final_tbl %>% 
  kbl(col.names = c("Species",
                    "# Correctly Classified",
                    "# Incorrectly Classified",
                    "% Correctly Classified")) %>% 
  kable_styling("hover", full_width = F)
         
```


#### Data citation

Abrahamson, W.G. 2019. Survival, growth and biomass estimates of two dominant palmetto species of south-central Florida from 1981 - 2017, ongoing at 5-year intervals ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/f2f96ec76fbbd4b9db431c79a770c4d5
