---
title: CV
name: Larissa
surname: Neilson
position: "Master's student"
location: "Goleta, CA"
phone: 818 282 6200
email: "eneilson@bren.ucsb.edu"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

## Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bachelor of Environmental Science", "2015-2019", "California State University, Monterey Bay", "Seaside, California",
  "Master of Environmental Science & Management", "In progress", "Bren School of Environmental Science & Management, UCSB", "Santa Barbara, California") %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Research Experience

**Research Assistant** (*in progress*)
  University of California, Santa Barbara
  Supervisor: Dr. Anastasia Quinatana

**Undergraduate Researcher** (6/18-8/18)  
Monterey Bay Aquarium Research Institute (MBARI)  
Supervisors: Dr. Steve Litvin, Dr. Jim Barry  

Analyzed and quantified the effects of climate change and ocean acidification associated with upwelling on juvenile Haliotis rufescens (red abalone) through an 8-week active experiment for an NSF project  

Organized and updated Excel worksheets with experiment data of all 300+ individuals  

Conducted extensive image and statistical analysis using experimental data from 300+ individuals  

Presented results to audiences ranging from 5-200 people at various conferences and symposiums including SACNAS and the California Central Coast Chapter of The Wildlife Society’s Annual Symposium  

## Field/Volunteer Experience


